\vspace*{-1.5em} \rule{\textwidth}{0.4pt} \\[0.4em] \textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification} \\[0.4em] \rule{\textwidth}{0.4pt}

### 2025-01-20 paper/main.tex
revised section 3

Overall, these plots confirm that \texttt{ZKLoRA} can handle large-scale implementation of LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.

@@

%------------------------------------------
% 3. ZKLoRA
%------------------------------------------
\section{ZKLoRA}
We implement a protocol that not only supports multi-party inference with partial activations exchanged between a base model user and a LoRA contributor, but also produces cryptographic proofs that the LoRA transforms are valid. First, the base model user processes any submodules that do not require LoRA directly on local hardware, sending partial activations only when a submodule contains LoRA-related layers. These exchanged activations, shown conceptually in Figure~\ref{fig:zklora_3steps}, correspond to “Base Acts” from the base model user and “LoRA Acts” from the LoRA contributor. Figure~\ref{fig:remote-lora-flow} also provides a fine-grained, computational perspective of what occurs when a submodule interfaces with remote LoRA weights.

Once the multi-party inference completes, the LoRA contributor shifts to a proof generation phase. At this stage, each LoRA module is compiled into a constraint system describing the LoRA transformations, and a key setup procedure yields the proving key, verification key, and possibly a structured reference string if the underlying zero-knowledge scheme requires one. The contributor then creates a “witness” by running partial activations through these constraints and finally produces the proof files. This entire flow is summarized in Algorithm~\ref{alg:zklora_concise}, where Step 1 covers the multi-party inference, Step 2 addresses proof generation, and Step 3 handles the final verification check.

Once the proof generation is done, the base model user receives each proof and runs a fast verification procedure, typically requiring about 1--2 seconds per module. As Figure~\ref{fig:remote-lora-flow} suggests, this does not require the LoRA contributor to reveal the actual low-rank matrices. Instead, the contributor only sends updates and proofs that these updates conform to the declared LoRA transformations. If any single proof fails, the base model user can reject the entire LoRA submission; otherwise, the system is accepted as consistent with the underlying base model. This design reflects the synergy between LoRA’s parameter-efficiency and zero-knowledge cryptographic protocols: LoRA significantly shrinks the parameter footprint being proven, while the zero-knowledge aspect maintains confidentiality of the contributor’s proprietary weights. By merging these ideas, \texttt{ZKLoRA} enables trust-driven collaboration across decentralized infrastructures, contract-based training, and other scenarios where proof-of-correctness is essential but the LoRA code remains private. Our approach also builds on incremental verification concepts \cite{valiant2008incrementally} and advanced proof systems such as Nova \cite{kothapalli2022nova} and HyperNova \cite{kothapalli2024hypernova}, which allow us to scale proofs to large neural networks. Ultimately, this combination provides a practical pipeline for parameter-efficient fine-tuning while verifying correctness in a succinct and minimally intrusive manner.

@@

\end{algorithmic}
\end{algorithm}

>>>>

Overall, these results confirm that \texttt{ZKLoRA} can handle large-scale implementation of LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.

@@

%------------------------------------------
% 3. ZKLoRA
%------------------------------------------
\section{ZKLoRA}
\texttt{ZKLoRA}'s design reflects the synergy between LoRA’s parameter-efficiency and zero-knowledge cryptographic protocols: LoRA significantly shrinks the parameter footprint being proven, while the zero-knowledge aspect maintains confidentiality of the contributor’s proprietary weights. By merging these ideas, \texttt{ZKLoRA} enables trust-driven collaboration across decentralized infrastructures, contract-based training, and other scenarios where proof-of-correctness is essential but the LoRA code remains private. Our approach also builds on incremental verification concepts \cite{valiant2008incrementally} and advanced proof systems such as Nova \cite{kothapalli2022nova} and HyperNova \cite{kothapalli2024hypernova}, which allow us to scale proofs to large neural networks. Ultimately, this combination provides a practical pipeline for parameter-efficient fine-tuning while verifying correctness in a succinct and minimally intrusive manner.

We implement a protocol that not only supports multi-party inference with partial activations exchanged between a base model user and a LoRA contributor, but also produces cryptographic proofs that the LoRA transforms are valid. The overall workflow is shown in Figure~\ref{fig:zklora_3steps}, while Figure~\ref{fig:remote-lora-flow} gives a deeper look at how Multi-Party Inference with LoRAs functions within an individual module. In addition, pseudocode for \texttt{ZKLoRA} is in Algorithm~\ref{alg:zklora}. To begin the Multi-Party Inference, the base model user puts the dataset chosen for inference into the base model's first module. The forward pass continues through until the base model until it hits a module that uses remote LoRA weights. When this occurs the base model user sends partial activations to the LoRA contributor for processing. These exchanged activations, shown conceptually in Figure~\ref{fig:zklora_3steps}, correspond to “Base Acts” from the base model user and “LoRA Acts” from the LoRA contributor.
%processes any submodules that do not require LoRA directly on local hardware, sending partial activations only when a submodule contains LoRA-related layers. These exchanged activations, shown conceptually in Figure~\ref{fig:zklora_3steps}, correspond to “Base Acts” from the base model user and “LoRA Acts” from the LoRA contributor. Figure~\ref{fig:remote-lora-flow} also provides a fine-grained, computational perspective of what occurs when a submodule interfaces with remote LoRA weights.

After the multi-party inference finishes, the LoRA contributor shifts to a proof generation phase. At this stage, each LoRA module is compiled into a constraint system describing the LoRA transformations, and a key setup procedure yields the proving key, verification key, and possibly a structured reference string if the underlying zero-knowledge scheme requires one. The contributor then creates a “witness” by running partial activations through these constraints and finally produces the proof files. %This entire flow is summarized in Algorithm~\ref{alg:zklora_concise}, where Step 1 covers the multi-party inference, Step 2 addresses proof generation, and Step 3 handles the final verification check.

Once the proof generation is done, the base model user receives each proof and runs a fast verification procedure, typically requiring about 1--2 seconds per module. As Figure~\ref{fig:remote-lora-flow} suggests, this does not require the LoRA contributor to reveal the actual low-rank matrices. Instead, the contributor only sends updates and proofs that these updates conform to the declared LoRA transformations. If any single proof fails, the base model user can reject the entire LoRA submission; otherwise, the system is accepted as consistent with the underlying base model.

@@

\end{algorithmic}
\caption{\texttt{ZKLoRA} Pseudocode }
\label{alg:zklora}
\end{algorithm}
